---
title: "Hello R"
author: "Thu Nguyen"
date: "Data 2401"
output: 
  html_document: 
    fig_width: 9
    fig_height: 8
    highlight: espresso
    theme: cosmo
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

According to the data table, there are 3 columns (dataset, x, and y) and 1846 rows that the datasaurus_dozen file have.


### Exercise 2

Plot `y` vs.`x` for the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Plot `y` vs.`x` for the star dataset:

```{r plot-star}
star_data <- datasaurus_dozen%>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes (x = x, y = y)) + geom_point()
```

Correlation between `x` and `y` in this dataset:
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x,y))
```

Compare to the r of dino which is -0.0645, the r of star is -0.0630 which is slightly larger. But they both have negative correlation between `x` and `y`.

### Exercise 4

Plot `y` vs.`x` for the circle dataset:

```{r plot-circle}
circle_data <- datasaurus_dozen%>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes (x = x, y = y)) + geom_point()
```

Correlation between `x` and `y` in this dataset:

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x,y))
```

Compare to the r of dino which is -0.0645, the r of circle is -0.0683 which is smaller. But they both have negative correlation between `x` and `y`.

### Exercise 5

Plot `y` vs.`x` for the all datasets:

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) + 
  geom_point() +
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

Correlation between `x` and `y` in all datasets:

```{r}
datasaurus_dozen%>%
  group_by(dataset)%>%
  summarize(r = cor(x,y))
```